Appendix B: Code for analysis comparing to historical data

### 2018-07-31 appendix/appendixB.Rmd
no author (double-blind)
Figure numbers, sp
fix eqn, sp

---
title: "Appendix B: Code for analysis comparing to historical data"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

Let's filter out missing data, non-matching units, and obvious reporting errors (catch exceeding total spawning biomass), then we rescale each series into the 0,1 by appropriate choice of units:

@@

```{r}
## Classic Graham-Schaefer. Note that recruitment occurs *before* harvest
gs <- function(r,K){
  function(x, h){ 
    x + x * r * (1 - x / K) - pmin(x,h)
  }
}
reward_fn <- function(x,h) pmin(x,h)
discount <- .95
```

>>>>

---
title: "Appendix B: Code for analysis comparing to historical data"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

Let's filter out missing data, non-matching units, and obvious reporting errors (catch exceeding total spawning biomass), then we re-scale each series into the 0,1 by appropriate choice of units:

@@

```{r}
## Classic Gordon-Schaefer. Note that recruitment occurs *before* harvest
gs <- function(r,K){
  function(x, h){ 
    x + x * r * (1 - x / K) - pmin(x,h)
  }
}
reward_fn <- function(x,h) pmin(x,h)
discount <- .95
```
